---
title: "tidy tuesday 2022-10-11"
author: "Scout Leonard"
date: "10/11/2022"
output: html_document
---

# Tidy Tuesday 2022: Week 41

[Tidy Tuesday](https://github.com/rfordatascience/tidytuesday) is a weekly event in which R users summarize and arrange data meaningfully using raw data shared by the [R4DS Online Learning Community](https://r4ds.had.co.nz/index.html).

For this week's Tidy Tuesday, I got to play with Ravelry data! This is especially exciting for me because I am a Ravelry user of ~7 years. I had a joyful time exploring this yarn rating data and thinking about how to visualize it. 

## Load Libraries 

```{r}
if (!require(librarian)) {
  install.packages("librarian")
  library(librarian)
}

shelf(here,
      tidyverse,
      ggimage)
```


## Pull Data

```{r}
tuesdata <- tidytuesdayR::tt_load(2022, week = 41)

yarn <- tuesdata$yarn
```

## Explore Data

```{r}
#all data 
nrow(yarn)
#100000

length(unique(yarn$name))
#72541

# what about yarn i can actually buy?? 
yarn_avail <- yarn %>% 
  filter(discontinued == "FALSE")

#ok, how much now??
nrow(yarn_avail)
#64289
```

## Data Viz!

### Process Data for Viz: 

Below, I make a list of the companies that Spinrite, Inc., a craft conglomerate, owns. I got this information from [their website](https://www.spinriteyarns.com/about-us). I am curious about which of the top 20 reviewed are Spinrite companies:

```{r}
spinrite_inc <- c("Anchor",
                  "Aunt Lydia's",
                  "Bernat",
                  "Caron",
                  "Coats & Clark",
                  "Lily",
                  "Patons North America",
                  "Peaches & Creme",
                  "Phentex",
                  "Red Heart",
                  "Susan Bates",
                  "wonderart")

yarn_avail_most_used <- yarn_avail %>% 
  arrange(desc(rating_count)) %>% 
  slice(1:20) %>% 
  mutate(spinrite_inc_owned = ifelse(yarn_company_name %in% spinrite_inc,
                                "Yes",
                                "No"))
```

### Assign plot elements

Below, I assign image and text elements to be used as layers in my final plot:

```{r}
#labels
label_1 <- "Tidy Tuesday 2022, Week 41 | Data Source: Ravelry | @scoutcleonard"

label_2 <- "Data include the top 20 yarns from Ravelry by total number of ratings.\nNumber of ratings for yarns pictures range from 39,000 to 97,000 reviews. \n Spinrite, Inc. is a craft conglomerate which owns several yarn companies which top yarn use according to Ravelry."

#images
star <- here("docs/2022/2022-10-11/star_2.png")
```

### Put it all together!

```{r}
#base plot
p <- ggplot(data = yarn_avail_most_used,
       aes(x = reorder(name, rating_average),
           y = rating_average,
           fill = spinrite_inc_owned)) +
  scale_fill_manual(values = c("#973d21", "#ee956a")) +
  geom_bar(stat = "identity") +
  coord_flip() +
  theme_minimal(base_family = "Roboto Condensed")

p_aesthetic <- p +
  labs(y = "Average Rating /5 Stars",
       title = "Ravelry's Most Frequently Reviewed Yarns",
       subtitle = "How Are They Rated?",
       caption = c(label_1, label_2)) +
  geom_image(mapping = aes(y = rating_average + 0.2,
                 x = name),
             image = star_2) +
  geom_text(data = yarn_avail_most_used,
            mapping = aes(y = rating_average + 0.2,
                          x = name,
                          label = rating_average),
            size = 2,
            color = "#133e7e") +
  geom_text(data = yarn_avail_most_used,
            mapping = aes(y = rating_average / 2,
                          x = name,
                          label = paste0(yarn_company_name, " - ", name)),
            size = 3,
            color = "white",
            family = "Roboto") +
  guides(fill = guide_legend(title = "Owned by Spinrite, Inc.?")) +
  theme(panel.background = element_rect(fill = "white",
                                        color = "white"),
        plot.background = element_rect(fill = "white",
                                       color = "white"),
        panel.grid = element_blank(),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        axis.title.y = element_blank(),
        plot.title = element_text(hjust = 0.5,
                                  color = "#133e7e",
                                  face = "bold"),
        plot.subtitle = element_text(hjust = 0.5,
                                  color = "#133e7e"),
        axis.title.x = element_text(color = "#133e7e",
                                    face = "bold"),
        legend.title = element_text(color = "#133e7e"),
        legend.text = element_text(color = "#133e7e"),
        plot.caption = element_text(hjust = c(0, 1),
                                    color = "#133e7e",
                                    size = 7),
        legend.position = "left") 
```

### Save final Plot

```{r}
ggsave(plot = p_aesthetic, 
       filename = "ravelry.png",
       path = here("viz"),
       width = 10,
       height = 7)
```

